Detecting Facial Expressions in Professional Tennis Matches

### 2017-02-13 Report06-12.Rmd
Table formatting

---
title: "Detecting Facial Expressions in Professional Tennis Matches"
author: "Stephanie Kobakian, Mitchell O'Hara-Wild, Dianne Cook, Stephanie Kovalcik"
date: '2017'
output: bookdown::pdf_document2
fontsize: 11pt
documentclass: article
bibliography: references.bib
---

```{r cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#packages:
library(bookdown)
library(pander)
library(ggplot2)
library(imager)
library(devtools)
library(knitcitations)
library(RefManageR)
library(readr)
library(knitr)
library(grid)
library(tidyverse)
library(magick)
library(kfigr)
library(UpSetR)
library(descr)
library(tables)

@@

```{r Scene-Attributes-Table, fig.cap ="\\label{tab:Scene-Attributes-Table}"}
kable(SceneAttributes, format = "pandoc", booktabs = TRUE, caption = "Attributes of a Scene of an image. The most appropriate option from the list was selected for each attribute.")
```

@@

```{r Solution-Specifications-Table, results='asis', fig.cap = "\\label{tab:Solution-Specifications-Table}"}
kable(SolutionSpecs, format = "pandoc", booktabs = TRUE)

@@

```{r Face-Attribute-Tables, results='asis', fig.cap = "Attributes of an individual face within an image. The most appropriate option from the list was selected for each attribute.\\label{tab:Face-Attribute-Tables}"}
kable(FaceAttributes, format = "pandoc", booktabs = TRUE)
```

####Manual Annotation
To record the details of attributes for each face and scene a Shiny [-@shiny] App was created. We called this Application our ManualClassificationProgram^[https://github.com/mvparrot/face-recognition/blob/master/ManualClassificationProgram.R]. This helped to provide information for all attributes quickly and consistently.
The Shiny [@shinyw] package provides a 'framework for building web applications using R'. It allows for the creation of web applications using R rather than 'requiring HTML, CSS, or JavaScript knowledge.'

The program we created was an interactive application that worked by presenting an image, using the imager @imager package, from the sample of images that had not yet been considered, appearing underneath were a set of radio buttons corresponding to the Scene Attributes in \@ref(tab:Scene-Attributes-Table) as shown above.

@@

@@

```{r Type-Matches-Manual, fig.cap = "\\label{tab:Type-Matches-Manual}"}

NoManual<-ALLmetaIMG %>% filter(ALLmetaIMG$type!="Manual")
NoManual<-NoManual %>% droplevels(NoManual$type) 
Accuracy<-with(NoManual, table(NoManual$matchesManual, NoManual$type))
CrossTable(Accuracy, prop.chisq = FALSE, cell.layout = TRUE, digits=4)
```

@@

```{r Image-Characteristics-Table, fig.cap = "\\label{tab:Image-Characteristics-Table}"}
ImageCharacteristics <- ALLmetaIMG %>% filter(type=="Manual") %>% group_by(situation, bg, shotangle, detect) %>% dplyr::summarise(count=n())
ImageCharacteristics<-arrange(ImageCharacteristics, desc(count))
ImageCharacteristics<-ImageCharacteristics[1:10,]
kable(ImageCharacteristics, booktabs = TRUE)
```

@@

GoogleNoMatch<-arrange(GoogleNoMatch, desc(count))
kable(GoogleNoMatch[1:10,], type = 'table')

@@

```{r Face-Characteristics-Table, fig.cap = "\\label{tab:Face-Characteristics-Table}"}
FaceCharacteristics <- ALLmetaIMGPlayers %>%   filter(type=="Google")%>% filter(matchesManual==TRUE)%>% group_by(visorhat, glasses, headangle, lighting, obscured, detect) %>% dplyr::summarise(count=n())
FaceCharacteristics<-arrange(FaceCharacteristics, desc(count))
FaceCharacteristics<-as.tbl(FaceCharacteristics[1:10,])
kable(FaceCharacteristics, type = 'table')
```

@@

```{r Accuracy}
Accuracy<-with(ALLmetaIMG, table(ALLmetaIMG$matchesManual, ALLmetaIMG$type))
kable(Accuracy)
# make this a proportional table, would this be necessary if we have the UpSetR
```

@@

kable(GoogleCharacteristics, format = "pandoc", booktabs = TRUE)
```

>>>>

---
title: "Detecting Facial Expressions in Professional Tennis Matches"
author: "Stephanie Kobakian, Mitchell O'Hara-Wild, Dianne Cook, Stephanie Kovalcik"
date: "13 February 2017"
output: bookdown::pdf_document2
fontsize: 11pt
documentclass: article
bibliography: references.bib
---

```{r cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#packages:
library(bookdown)
library(pander)
library(ggplot2)
library(imager)
library(devtools)
library(knitcitations)
library(RefManageR)
library(readr)
library(knitr)
library(grid)
library(tidyverse)
library(magick)
library(kfigr)
library(UpSetR)
library(descr)
library(tables)
library(xtable)

@@

```{r Scene-Attributes-Table, fig.cap ="\\label{tab:Scene-Attributes-Table}"}
kable(SceneAttributes, format = "markdown", booktabs = TRUE, caption = "Attributes of a Scene of an image. The most appropriate option from the list was selected for each attribute.")
```

@@

```{r Solution-Specifications-Table, fig.cap = "\\label{tab:Solution-Specifications-Table}", results='asis',}
kable(SolutionSpecs, format = "markdown", booktabs = TRUE, caption="")
```

@@

```{r Face-Attribute-Tables, results='asis', fig.cap = "Attributes of an individual face within an image. The most appropriate option from the list was selected for each attribute.\\label{tab:Face-Attribute-Tables}"}
kable(FaceAttributes, format = "markdown", booktabs = TRUE)
```

####Manual Annotation
To record the details of attributes for each face and scene a Shiny [-@shiny] App was created. We called this Application our ManualClassificationProgram^[https://github.com/mvparrot/face-recognition/blob/master/ManualClassificationProgram.R]. This helped to provide information for all attributes quickly and consistently.

@@

```{r Regression, fig.cap = "\\label{Regression}"}
hitmiss <- function(x){
  allType <- c("Animetrics", "Google", "Microsoft", "Skybiometry")
  hit <- allType %in% x$type
  x[1,] %>%
    dplyr::select(file:visorhat) %>%
    cbind(type = allType, hit = hit)
}

glmFits <- ALLmetaIMGFaces %>%
  split(.$FaceKey) %>%
  map_df(~ hitmiss(.)) %>%
  split(.$type) %>%
  map(~ glm(hit ~ ., data = select(., -type, -file), family=binomial(link='logit')))

glmSummary <- glmFits %>%
  map(~ rename(cbind(rownames_to_column(cbind(as.data.frame(coef(summary(.)))))), variable = rowname))

glmPlot <- do.call(rbind, Map(cbind, glmSummary, type = names(glmSummary)))

## Significance of variables by software
#glmPlot %>%
#  mutate(significant = `Pr(>|t|)` < 0.05) %>%
#  filter(significant==TRUE) %>% 
#  droplevels(glmPlot$variable) %>% 
#  ggplot(aes(x=type, y=`Pr(>|t|)`)) + 
#  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
#  geom_col(aes(fill=significant))

glmx <- glmPlot %>%
  mutate(significant = `Pr(>|z|)` < 0.05) %>%
  filter(significant==TRUE) %>% 
  droplevels(glmPlot$variable) %>% 
  ggplot(aes(x=variable, y=`Pr(>|z|)`)) + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  geom_col(aes(fill=type)) 
glmx

This shows how influential certain attributes are in determining whether a face will be detected or not.

Regression analysis showed

@@

```{r Type-Matches-Manual, fig.cap = "\\label{tab:Type-Matches-Manual}"}
NoManual<-ALLmetaIMG %>% filter(ALLmetaIMG$type!="Manual")
NoManual<-NoManual %>% droplevels(NoManual$type) 
Accuracy<-with(NoManual, table(NoManual$matchesManual, NoManual$type))
ct<-CrossTable(Accuracy, prop.chisq = FALSE, cell.layout = TRUE, digits=4)
print(ct)
```

@@

```{r Image-Characteristics-Table, fig.cap = "\\label{tab:Image-Characteristics-Table}"}
ImageCharacteristics <- ALLmetaIMG %>% filter(type=="Manual") %>% group_by(situation, bg, shotangle, detect) %>% dplyr::summarise(count=n())
ImageCharacteristics<-arrange(ImageCharacteristics, desc(count))
ImageCharacteristics<-ImageCharacteristics[1:10,]
kable(ImageCharacteristics, booktabs = TRUE, caption="", format = "markdown")
```

@@

GoogleNoMatch<-arrange(GoogleNoMatch, desc(count))
kable(GoogleNoMatch[1:10,], caption="", format = "markdown")

@@

```{r Face-Characteristics-Table, fig.cap = "\\label{tab:Face-Characteristics-Table}"}
FaceCharacteristics <- ALLmetaIMGPlayers %>%
  filter(type=="Google") %>%
  filter(matchesManual==TRUE) %>%
  group_by(visorhat, glasses, headangle, lighting, obscured, detect) %>% dplyr::summarise(count=n())

FaceCharacteristics<-arrange(FaceCharacteristics, desc(count))
FaceCharacteristics<-as.tbl(FaceCharacteristics[1:10,])
kable(FaceCharacteristics, caption="", format = "markdown")
```

@@

```{r Accuracy}
Accuracy<-with(ALLmetaIMG, table(ALLmetaIMG$matchesManual, ALLmetaIMG$type))
kable(Accuracy, caption="", format = "markdown")
# make this a proportional table, would this be necessary if we have the UpSetR
```

@@

kable(GoogleCharacteristics, format = "markdown", booktabs = TRUE, caption="")
```
